SecureIt\\ Wireless networks project\\ 2012/2013

### 2012-12-26 relazioni/wireless/paper.tex
Aggiunta sezione 'Data representation' per microfono

\begin{enumerate}
	\item Asks the application to use the accelerometer, shown only if the accelerometer is available on the phone
	\item Asks the application to use the camera, allows to choose wich camera to use and to start the flash
	\item Asks the application to use the microphone
	\item Asks the application to send an SMS to the specified phone number to alert an intrusion
	\item Asks the application to authenticate and send images, audio and location to the back-end (images are sent only if camera has been activated). A username and a password have to be specified
	\item Allows to set the unlock code. Application can be closed only by writing that code
\end{enumerate}

@@

>>>>

\begin{enumerate}
	\item Asks the application to use the accelerometer, shown only if the accelerometer is available on the phone
	\item Asks the application to use the camera, allows to choose which camera to use and to start the flash
	\item Asks the application to use the microphone
	\item Asks the application to send an SMS to the specified phone number to alert an intrusion
	\item Asks the application to authenticate and send images, audio and location to the back-end (images are sent only if camera has been activated). A username and a password have to be specified
	\item Allows to set the unlock code. Application can be closed only by writing that code
\end{enumerate}

@@

To make the end user understand what the application is doing a view shows the decibels sampled by the microphones. The values are represented using a two channel volume indicator (in case of stereo microphones owned by some devices). Two levels are highlighted in the indicator: the first one is the threshold over which an alert is fired while the second one is an arbitrary noyse threshold.

\begin{figure}[!ht]
\begin{center}
\makebox[\linewidth]{\includegraphics[scale=0.3]{resources/microphone.png}}
\caption{Microphone view to show sampled audio level}
\label{img:microphone}
\end{center}
\end{figure}
